Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Fixed caption of depth-masking screenshot
Say 'approach' in screenshot captions for approaches
Say 'on some systems' when talking about performance boost of optimized slicing

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot.png}
\caption{Screenshot of Boolean AND.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot.png}
\caption{Screenshot of Boolean XOR.}
\end{figure}

@@

As a baseline the Boolean-based approaches were compared to the existing
view-aligned slicing method from previous work by developing a simple prototype.
To be fair, a variation of the slicing method optimized for two volumes was
created.  Basically rather than using uniform variables to switch textures as
would normally be done, the optimized variation stores the texture with each
vertex instead.  While it requires a fairly significant amount of extra storage,
using vertex attributes allows all the slices to be transferred to the card at
once.  The result is a considerable performance boost, similar to how it is
generally faster to transfer one large file across a network then many small
ones.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot.png}
\caption{Screenshot of Depth-Masking approach.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot.png}
\caption{Screenshot of Boolean XOR approach.}
\end{figure}

@@

As a baseline the Boolean-based approaches were compared to the existing
view-aligned slicing method from previous work by developing a simple prototype.
To be fair, a variation of the slicing method optimized for two volumes was
created.  Basically rather than using uniform variables to switch textures as
would normally be done, the optimized variation stores the texture with each
vertex instead.  While it requires a fairly significant amount of extra storage,
using vertex attributes allows all the slices to be transferred to the card at
once.  The result is a considerable performance boost on some systems, similar
to how it is generally faster to transfer one large file across a network then
many small ones.
